\documentclass{article}

\usepackage{float}
\restylefloat{table}

\usepackage{booktabs}

\title{Team Contributions: Final\\\progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

This document summarizes the contributions of each team member for the final
demonstration and documentation.

\section{Team Meeting Attendance}


\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 4\\
Jake Read & 4\\ %
Sunny Yao & 4\\ %
Rebecca Di Filippo & 4\\ %
Matthew Cheung & 4\\ %
\bottomrule
\end{tabular}
\end{table}

Most of team communication was done asynchronously via our project channel, so fewer formal meetings were needed.

\section{Supervisor/Stakeholder Meeting Attendance}


\noindent \textbf{Supervisor's Name: } Istvan David %

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 5\\
Jake Read & 5\\ %
Sunny Yao & 5\\ %
Rebecca Di Filippo & 5\\ %
Matthew Cheung & 5\\ %
\bottomrule
\end{tabular}
\end{table}


\section{Lecture Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 1\\
Jake Read & 1\\ %
Sunny Yao & 0\\ %
Rebecca Di Filippo & 0\\ %
Matthew Cheung & 0\\ %
\bottomrule
\end{tabular}
\end{table}

Jake attended the one lecture and took notes for the rest of the team, who reviewed the lecture materials on their own time.

\section{TA Document Discussion Attendance}


\noindent \textbf{TA's Name: } Tiago de Moraes Machado %

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 1\\
Jake Read & 1\\ %
Sunny Yao & 1\\ %
Rebecca Di Filippo & 1\\ %
Matthew Cheung & 1\\ %
\bottomrule
\end{tabular}
\end{table}


\section{Commits}


\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Commits} & \textbf{Percent}\\
\midrule
Total & 502 & 100\% \\
Jake Read & 125 & 25\% \\ %
Sunny Yao & 102 & 20\% \\ %
Rebecca Di Filippo & 192 & 38\% \\ %
Matthew Cheung & 84 & 17\% \\ %
\bottomrule
\end{tabular}
\end{table}


The difference in commits is not indicative of productivity or contribution.
It is due to commit styles, where some members choose to commit more often than others.


\section{Issue Tracker}


\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Authored (O+C)} & \textbf{Assigned (C only)}\\
\midrule
Jake Read & 10 & 12 \\ %
Sunny Yao & 6 & 4 \\ %
Rebecca Di Filippo & 7 & 6 \\ %
Matthew Cheung & 4 & 4 \\ %
\bottomrule
\end{tabular}
\end{table}

Some issues assigned were much more complex than others, which can explain the difference in numbers.


\section{Team Charter Trigger Items}

\textbf{Trigger Summary:}
Based on our team charter, the primary triggers for intervention include:  %
\begin{itemize}
\item Missing a scheduled meeting without at least 12 hours notice  %
\item Repeated missed deadlines with little or no advance communication (more than 1--2 times)  %
\item Consistently arriving late without notice  %
\item Not contributing adequately or submitting low-quality work  %
\item Disruptive behavior or conflict without an attempt to resolve collaboratively  %
\end{itemize}

\textbf{Observed Trigger Events:}
No formal trigger violations occurred during this period.
A few scheduling conflicts were communicated ahead of time and aligned with acceptable reasons outlined in the charter.
These included:
\begin{itemize}
\item A member needing to leave a meeting early due to a prior communicated commitment
\end{itemize}
All instances were communicated prior to the meeting or work session and did not impact project progress.
\medskip{}

\textbf{Plan and Reflection:}
No corrective action was necessary, as all situations fell under acceptable charter guidelines and were handled responsibly. The team will continue to:
\begin{itemize}
\item Communicate scheduling conflicts in advance
\item Support academic and personal commitments when reasonable
\item Maintain fairness, accountability, and consistent participation
\end{itemize}
Our current triggers appear appropriate and do not require revision at this time.


\section{Additional Productivity Metrics}

No additional metrics were tracked during this period.

\end{document}