\documentclass{article}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{float}
\usepackage{hyperref}

\title{User Review Summary for the Instructional Video\\\progname}
\author{\authname}
\date{}

\input{../../Comments}
\input{../../Common}

\begin{document}

\maketitle

\tableofcontents

\listoftables

\newpage

\begin{table}[hp]
\caption{Revision History} \label{TblRevisionHistory}
\begin{tabularx}{\textwidth}{llX}
\toprule
\textbf{Date} & \textbf{Developer(s)} & \textbf{Change}\\
\midrule
Apr 7th 2026 & All & Full breakdown for Final Doc submission.\\
\bottomrule
\end{tabularx}
\end{table}

\newpage

\section{Introduction}

To get a general sense of how useful the instructional video was, a small set of
informal user reviews was collected. Users were asked to use the video while
navigating the Catan Arena platform, including setting up Bot vs.\ Bot matches,
playing a game against a bot, and using the replay and explanation features.

This write-up is not intended to be a full usability study. Instead, it provides a
quick summary of whether the video was generally enough to help users get started
without needing someone to walk them through the site.

\section{Review Summary}

Table~\ref{tab:review-summary} summarizes the ratings provided by the seven users
included in this summary.

\begin{table}[H]
\centering
\caption{Summary of User Ratings}
\label{tab:review-summary}
\begin{tabularx}{0.75\textwidth}{lXc}
\toprule
\textbf{User} & \textbf{General Impression} & \textbf{Rating} \\
\midrule
User 1 & Quick, clear, and easy to follow & 5/5 \\
User 2 & Mostly helpful, but the replay section moved too fast & 3/5 \\
User 3 & Beginner-friendly and enough to get started confidently & 5/5 \\
User 4 & Well made overall, with one or two missing details & 4/5 \\
User 5 & Easy to follow and useful for both gameplay and replay & 5/5 \\
User 6 & Strong explanation of the replay and move-breakdown features & 4/5 \\
User 7 & Good setup instructions, but replay was less smooth on tablet & 3/5 \\
\midrule
\multicolumn{2}{r}{\textbf{Average Rating}} & \textbf{4.14/5} \\
\bottomrule
\end{tabularx}
\end{table}

\section{Individual User Reviews}

\subsection{User 1 --- Rating: 5/5}

\begin{itemize}
    \item I usually skip tutorial videos, but this one was short enough that I actually watched it.
    \item I got a Bot vs.\ Bot match running pretty quickly just by copying what it showed.
    \item Seeing the AI play first made it easier to understand where everything was before I started clicking around myself.
    \item The replay section was also useful, since I probably would not have noticed that button on my own.
\end{itemize}

\subsection{User 2 --- Rating: 3/5}

\begin{itemize}
    \item The first part of the video was easy enough to follow, but it sped up a lot once it got to replay.
    \item I did not realize right away that I had to click the move text itself to open the explanation.
    \item Once I found it, the explanation feature was actually pretty useful.
    \item That part of the video would be easier to follow with a clearer visual cue.
\end{itemize}

\subsection{User 3 --- Rating: 5/5}

\begin{itemize}
    \item I had not used the site before, and the video made it pretty easy to get started.
    \item I tried a normal game against an Easy bot and did not feel lost.
    \item The replay explanation feature helped a lot when I wanted to understand why a move happened.
    \item After watching the video once, I did not feel like I needed extra instructions.
\end{itemize}

\subsection{User 4 --- Rating: 4/5}

\begin{itemize}
    \item The video itself looked polished and the audio was clear.
    \item The replay analysis section was probably the most interesting part for me.
    \item I ended up spending quite a while clicking through moves just to see how the bots were playing.
    \item The only thing I noticed missing was that it did not really explain changing bot speed.
\end{itemize}

\subsection{User 5 --- Rating: 5/5}

\begin{itemize}
    \item It was easy to follow because it just showed someone using the actual interface.
    \item I played a game, then went back into replay to check why the bot had made a few choices.
    \item That part was especially helpful once the game got close near the end.
    \item Overall it felt straightforward and practical.
\end{itemize}

\subsection{User 6 --- Rating: 4/5}

\begin{itemize}
    \item I already know \emph{Catan}, so I mostly cared about the replay and explanation features.
    \item The video did a good job showing how to step through the game and inspect individual moves.
    \item I used it to look at early settlement placements and see what the bot seemed to value.
    \item That part of the site is one of the strongest features, and the video explained it fairly well.
\end{itemize}

\subsection{User 7 --- Rating: 3/5}

\begin{itemize}
    \item I was watching the video on my PC while using the site on my tablet, and that mostly worked fine.
    \item Starting a bot game was easy from the instructions.
    \item The only part that felt awkward was replay, since some of the buttons looked pretty small.
    \item I could still use it, but that section felt a bit less smooth than the rest.
\end{itemize}

\section{Observed Themes}

\subsection{Strengths}

A few strengths showed up consistently across the reviews:

\begin{itemize}
    \item Most users found the video easy to follow for starting a match.
    \item The Bot vs.\ Bot and standard gameplay setup were generally clear.
    \item Several users said the replay and explanation features were useful once they found them.
    \item A number of users felt the video was enough to get them started without needing extra help.
\end{itemize}

\subsection{Areas for Improvement}

The main issues mentioned across the reviews were:

\begin{itemize}
    \item The replay section was harder to follow than the rest of the video.
    \item It was not always obvious that users needed to click the move log text to open explanations.
    \item Some smaller controls, such as bot speed or replay-related buttons, were easy to miss.
    \item The current video works best on desktop, and some elements may be less clear on smaller screens.
\end{itemize}

Fixing these issues is currently considered out of scope given the time constraints, but they are worth noting for future improvements post-capstone.

\section{Conclusion}

Overall, the feedback suggests that the instructional video does a good job helping
new users get started with the platform, especially when it comes to setting up
matches and understanding the basic layout of the site. The replay and explanation
features were also seen as useful, but they were the part users seemed most likely
to miss or need a second look at.

The clearest next improvement would be to slow down the replay walkthrough and
make the explanation click target more visually obvious in the video.

\end{document}